Preparing for Potential Closure of European Airspaces due to Re-entering Space Objects

### 2025-06-09 paper.qmd
missing "which"

Of practical interest for the application of this work and future extension
is the scenario of mission failure at launch can typically lead to vast airspace
closure and traffic re-routing: The techniques developed would allow to
quantify risk and impact of the planned measures.

>>>>

Of practical interest for the application of this work and future extension
on casualty risk is the scenario of mission failure at launch
which can typically lead to vast airspace closure and traffic re-routing:
the techniques developed here  would help to quantify risk and impact of the
planned measures.
